### 2018-06-14 manuscript.tex
Update manuscript.tex

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
The main constructs to test the three theories of FGC practices(e.g., conventions, modernization, and feminism) are inferred from the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm).  The planned behavior theory proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, we constructed women's fgc attitudes based on the xx questions of FGC benefits in DHS, women's gender attitudes based on xx questions of domestic violence; the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.

>>>>

\subsubsection{Measurements and Concepts}\label{measurements-and-concepts}
---- benefirs of fgc is value (what fulfilment/benefits/positivity someone get by performing certain behaviors), not attitude,

The main constructs to test the three theories of FGC practices(e.g., conventions, modernization, and feminism) are inferred from the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm).  The planned behavior theory proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, we constructed women's fgc attitudes based on the xx questions of FGC benefits in DHS, women's gender attitudes based on xx questions of domestic violence; the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.
